Prove that a module $_RQ$ is injective if and only if for every left ideal $I$ of $R$ and every
$R$-homomorphism $f:I\to Q$ there is a homomorphsim $g:R\to Q$ with $g|_I=f$.\\\\

\begin{solution}\renewcommand{\qedsymbol}{}\ \\
    
    Let $_RQ$ be a module. Assume first that $_RQ$ is injective. Let $I\subseteq R$ be an ideal and let
    $f:I\to Q$ be an $R$-homomorphsim. Since $_RQ$ is injective, we have that for any two left
    $R$-modules $X,Y$ such that $\phi:X\to Y$ is an injective $R$-homomorphism, and $\psi:X\to Q$ is
    any $R$-homomorphism, then there exists and $R$-homomorphism $\rho:Y\to Q$ such that
    $\psi=\phi\rho$. In particular, we can look at the left $R$-modules $_RR$ and $_RIQ$. So, let
    $\phi:IQ\to R$ be an injective $R$-homomorphism, and $\psi:IQ\to Q$ be any $R$-homomorphism. Then,
    there exists an $R$-homomorphism $\rho:R\to Q$. Clearly, based on the construction, we have that
    $\rho|_I=f$ and since $I$ and $f$ were arbitrary, we have that the forward direction holds true.\\

    On the other hand, assume that for every left ideal $I\subseteq R$ and every $R$-homomorphism
    $f:I\to Q$ there is a homomorphism $g:R\to Q$ such that $g|_I=f$ where $Q$ is a left $R$-module. Let
    $N\subseteq M$ be left $R$-modules with $\gamma:N\to Q$ extending to $\gamma':M\to Q$. Using the
    partial ordering of subset equality, we envoke Zorn's Lemma to say that there exists a maximal
    element $\tilde{N}\subseteq M$ such that $\gamma$ extends to $\gamma':\tilde{N}\to Q$. If
    $\tilde{N}=M$, we are done. If $\tilde{N}\neq M$, then consider $\tilde{n}\in M\setminus\tilde{N}$.
    Further, consider the ideal $I$ of $R$ generated by $\tilde{n}$. Then, we have that $f:I\to Q$
    extends to $g:R\to Q$ by assumption. Observe that if we define $\lambda:\tilde{N}+R\tilde{n}\to Q$
    by $\lambda(n'+r\tilde{n})=\gamma'(n')+g(r)$, we contradict maximlaity. Therefore, $\tilde{N}=M$.
    As such, $Q$ is injective as a left $R$-module as desired.
 
\end{solution}