A left $R$-module $M$ is hopfian if any surjective $R$-endomorphism of $M$ is an automorphism.\\
a. Show that any noetherian module $M$ is hopfian.\\
b. Show that the left regular module $_RR$ is hopfian if and only if $R$ is Dedekind-finite.\\
c. Deduce from a and b above that any left noetherian ring $R$ is Dedekind-finite.\\

\begin{solution}\renewcommand{\qedsymbol}{}\ \\
    Let $R$ be a ring.\\

    a. Let $M$ be an arbitrary noetherian $R$-module, and let $f:M\rightarrow M$ be a surjective
    $R$-homomorphism. Since $M$ is noetherian, we have that the submodules of $M$ satisfy
    $N_1\subset N_2\subset\ldots\subset N_n=N_{n+1}=\ldots$ for some $n\in\mathbb{Z}^+$ where $N_i$ are
    $R$-submodules of $M$. Now, let $x\in N_1$ such that $f(x)=0$. Hence, $x\in N_i$ for all $i\geq1$.
    So, $f^n(x)=0$. That is, $x\in\ker(f^n)$. Now, we know from a previous problem that
    $f^n(M)\cap\ker(f^n)=\{0\}$. Therefore, we have that $x=0$. So, $f$ is $1-1$ and is thus an
    $R$-automorphism. Since $f$ was arbitrary, any surjective $R$-endomorphism is an $R$-automorphism.
    Whence, $M$ is hopfian as desired.\\

    b. Assume first that $_RR$ is hopfian. Let $a,b\in R$ such that $ab=1$. Let $\phi:M\rightarrow M$ be
    a surjective $R$-endomorphism. Since $_RR$ is hopfian, we have that $\phi$ is an automorphism. Since
    $ab=1$, $b\phi(ab)=\phi(b(ab))=\phi((ba)b)=ba\phi(b)=b\phi(1)=\phi(b)$ since $\phi$ is an
    automorphism. Hence, $ba=1$ and so $R$ is Dedkind finite. Now, assume that $R$ is Dedekind finite
    and let $\phi:M\rightarrow M$ be a surjective $R$-endomorphism. Let $a,b\in R$ such that $ab=1$, and
    assume that $\phi(a)=\phi(b)$. Since $R$ is Dedekind finite, we have that $ba=1$. So,
    $\phi(1)=\phi(ab)=\phi(ba)$. Since $\phi$ is a homomorphism, we get that $a\phi(b)=b\phi(a)$. By
    supposition, $\phi(a)=\phi(b)$, whence $a=b$ by cancellation on the right. Thus, $\phi$ is $1-1$ and
    since $\phi$ was an arbitrary surjective endomorphism, every such endomorphism is an automorphism.\\

    c. Let $R$ be a left noetherian ring. So we have that every left $R$-module of $R$ is noetherian. In
    particular, $_RR$ is noetherian. By part a, we have that $_RR$ is hopfian and by part b, we have
    that $R$ is Dedekind finite as desired.


\end{solution}