a. Show that a ring $R$ is semiprime iff, for any two ideals $A,B$ in $R$, $AB=0$ implies that 
$A\cap B=0$.\\
b. Let $A,B$ be left (resp. right) ideals in a semiprime ring $R$. Show that $AB=0$ iff $BA=0$. If $A$
is an ideal, show that $ann_r(A)=ann_l(A)$.\\

\begin{solution}\renewcommand{\qedsymbol}{}\ \\
    a. Let $R$ be a ring. Assume first that $R$ is semiprime. Let $A,B$ be ideal of $R$ such that
    $AB=0$. We may assume that $A,B\neq0$. Since $R$ is semiprime, we have that $\{0\}$ is a semiprime
    ideal, and there are no nonzero nilpotent ideals. Note that if $A=B$, then $AB=A^2=0$ and so $A=0=B$
    which means $A\cap B=0$. If $A\neq B$. Let $x\in A\cap B$ and observe $(BxA)^2$. Then,
    $(BxA)(BxA)=BxABxA=0$ since $AB=0$. So, $BxA=0$ since $R$ is semiprime. By supposition that
    $A,B\neq0$, we find that $x=0$ and since $x\in A\cap B$ was arbitrary, we have that $A\cap B=0$ as
    desired. On the other hand, assume that for any two ideals $A,B\subseteq R$ if $AB=0$, then
    $A\cap B=0$. Let $A$ be an ideal of $R$ and consider the situation $AA=A^2=0$. Then $A\cap A=A=0$ by
    our assumption. Then we see that $R$ has no nonzero nilpotnet ideals since $A$ was an arbitrary
    ideal. Thus, $R$ is semiprime as desired.\\

    b. Let $R, A$, and $B$ be as given above. Our argumnet will proceed as follows. Assume first that
    $AB=0$. Consider $(BA)^2$. This yields $(BA)(BA)=BABA$. Since we assume that $AB=0$, we have that
    $BABA=B0A=0$. Whence $BA=0$ from the fact that $R$ is semiprime. Next, assume that $BA=0$.
    Similarlly observe $(AB)^2=(AB)(AB)=ABAB$. By supposition, $BA=0$, and so $ABAB=A0B=0$. Thus, $AB=0$
    by $R$ being semiprime, completing our proof.\\
    
    Now, let $A$ be an arbitrary ideal of $R$. We will show that $ann_r(A)=ann_l(A)$. Our proof is as
    follows. We have that $ann_r(A)=\{r\in R|rA=0\}$ and $ann_l(A)=\{r\in R|Ar=0\}$. Let $r\in ann_r(A)$
    and examine $(Ar)^2$. This gives us $(Ar)(Ar)=ArAr$ and since we have that $rA=0$ by
    $r\in ann_r(A)$, $ArAr=0$. Hence, $Ar=0$ since $R$ is semiprime. Therefore, $r\in ann_l(A)$.
    Conversely assume that $r\in ann_l(A)$ and consider $(rA)^2$. Then, $(rA)(rA)=rArA$. So, $rArA=0$ by
    our assumption that $Ar=0$. Since $R$ is semiprime, $rA=0$ and we conclude that $r\in ann_r(A)$.
    Thus, $ann_r(A)=ann_l(A)$ as desired.

\end{solution}