(\#4 in 3.2) Find all the topologies on the set $X = \{a,b,c\}$. There are 29 of them. (Hint: be
extremely organized in how you write them down).\\\\

\begin{solution}\renewcommand{\qedsymbol}{}\ \\
    Let $X$ be as given above. Well, there are the two standard topologies, $D=\mathcal{P}(X)$ and
    $J=\{\emptyset, X\}$. Now, the three element topologies are:
    
    $$\{\emptyset, \{a\}, X\}, \{\emptyset, \{b\}, X\}, \{\emptyset, \{c\}, X\},
    \{\emptyset, \{a,b\}, X\},\{\emptyset, \{a,c\}, X\}, \{\emptyset, \{b,c\}, X\}$$
    
    Consider $\{\emptyset, \{a\}, X\}$. Clearly $\emptyset$ and $X$ are in the set and taking any
    arbitrary union or intersection will yield $\emptyset, \{a\},$ or $X$, so $\{\emptyset, \{a\}, X\}$
    is a topology on $X$. By similar logic, we have that all the three element sets are indeed
    topologies of $X$. Now, the four element topologies are:
    
    $$\{\emptyset, \{a\}, \{a,b\}, X\}, \{\emptyset, \{a\}, \{a,c\}, X\},
    \{\emptyset, \{a\}, \{b,c\}, X\}, \{\emptyset, \{b\}, \{a,b\}, X\},
    \{\emptyset, \{b\}, \{a,c\}, X\}$$
    $$\{\emptyset, \{b\}, \{b,c\}, X\}, \{\emptyset, \{c\}, \{a,b\}, X\},
    \{\emptyset, \{c\}, \{a,c\}, X\}, \{\emptyset, \{c\}, \{b,c\}, X\}$$
    
    To show this, take $\{\emptyset, \{a\}, \{a,b\} X\}$. Again, we see that $\emptyset$ and $X$ are in
    the set. Now, any union of any of the elements will give us $\emptyset, \{a\}, \{a,b\}$, or $X$.
    Similarly, any intersection would give us $\emptyset, \{a\}, \{a,b\}$, or $X$. Thus
    $\{\emptyset, \{a\}, \{a,b\}, X\}$ is a topology. Now consider $\{\emptyset, \{a\}, \{b,c\}, X\}$.
    Still, $\emptyset$ and $X$ are in this set and we see that any union or intersection will give us
    only $\emptyset$ or $X$. So $\{\emptyset, \{a\}, \{b,c\}, X\}$ is also a topology on $X$. Hence, by
    similar logic from either of the two previous cases, all of the four element sets are topologies on
    $X$, bringing the total to 17. Next, the five element topologies are:
    
    $$\{\emptyset, \{a\}, \{b\}, \{a,b\}, X\}, \{\emptyset, \{a\}, \{c\}, \{a,c\}, X\},
    \{\emptyset, \{b\}, \{c\}, \{b,c\}, X\}, \{\emptyset, \{a\}, \{a,b\}, \{a,c\}, X\}$$
    $$\{\emptyset, \{b\}, \{a,b\}, \{b,c\}, X\}, \{\emptyset, \{c\}, \{a,c\}, \{b,c\}, X\}$$
    
    From these five element sets, consider $\{\emptyset, \{a\}, \{b\}, \{a,b\}, X\}$. Now, $X$ and
    $\emptyset$ are in this set. Next if we take any arbitrary union in the set, we will always fall
    back in the set. Lastly, any finite intersection will also remain in the set. Thus,
    $\{\emptyset, \{a\}, \{b\}, \{a,b\}, X\}$ is a topology, and since all five elemenet sets are
    similar to this, they all are topologies. Finally, the six element topologies are:
    
    $$\{\emptyset, \{a\}, \{b\}, \{a,b\}, \{a,c\}, X\}, \{\emptyset,\{a\}, \{b\}, \{a,b\}, \{b,c\}, X\},
    \{\emptyset, \{a\}, \{c\}, \{a,b\}, \{a,c\}, X\}$$
    $$\{\emptyset,\{a\}, \{c\}, \{a,c\}, \{b,c\}, X\}, \{\emptyset, \{b\}, \{c\}, \{a,b\}, \{b,c\}, X\},
    \{\emptyset, \{b\}, \{c\}, \{a,c\}, \{b,c\}, X\}$$
    
    Since all of these six element sets contain $X$ and $\emptyset$ and are closed under unions and
    intersections, they are all topologies. Thus, we have all 29 topologies of $X$.

\end{solution}