Show that if $U$ is an open connected subset of $\mathbb{R}^2$, then $U$ is path-connected.
(Hint: Show that given a point $x_0\in U$, the set of points in $U$ that can be joined to $x_0$ by a
path in $U$ is both open and closed.)\\\\


\begin{solution}\renewcommand{\qedsymbol}{}\ \\
    Let $U$ be an open connected subset of $\mathbb{R}^2$. If $U=\mathbb{R}^2$, then $U$ is path
    connected. So, assume $U\subset\mathbb{R}^2$. Fix $(x_0,y_0)\in U$. Let $V$ be the set of points
    $(x,y)\in U$ such that $(x,y)$ can be joined to $(x_0,y_0)$ by a path in $U$. Then $V\subseteq U$
    and $V\neq\emptyset$ since $(x_0,y_0)\in V$. Now, let $(x,y)\in V$ and let $B_1$ be a basis set of
    $\mathcal{U}^2$ such that $(x,y)\in B_1$. Now, take $(x_1,y_1)\in B_1$ where $x\neq x_1$. Let
    $m=\frac{y_1-y}{x_1-x}$ and define $\alpha:[0,1]\rightarrow\mathbb{R}^2$ by $\alpha(t)=(x+mt,y+mt)$.
    Now, $p_x\circ\alpha=x+mt$ and $p_y\circ\alpha=y+mt$ are both continuous since they are both linear,
    and by Theorem 5.2.2, $\alpha$ is continuous. Hence, we have that $B_1$ is path connected. So, let
    $(x',y')\in B_1$ with $(x',y')\neq(x,y)$. Since $B_1$ is path-connected, $(x',y')$ can be joined to
    $(x,y)$ by a path and therefore can be joined to $(x_0,y_0)$ by a path. So, $(x',y')\in V$. Hence,
    $B_1\subseteq V$ and so $V$ is open. Now, let $(x,y)\in\mathbb{R}^2\setminus V$ and let $B_2$ be a
    basis set such that $(x,y)\in B_2$. Again, since $B_2$ is a basis set, $B_2$ is path-connected. Now,
    let $(x',y')\in B_2$. Since $B_2$ is path-connected, $(x',y')$ can be joined to $(x,y)$ by a path.
    So, $(x',y')\in\mathbb{R}^2\setminus V$ and hence $B_2\subseteq\mathbb{R}^2\setminus V$. So,
    $\mathbb{R}^2\setminus V$ is open and by definition, $V$ is closed. Since $U$ has a subset that is
    both open and closed and $U$ is connected, we have that $U=V$. Since $V$ is the set of all points
    $(x,y)\in U$ such that $(x,y)$ can be joined to $(x_0,y_0)$ by a path in $U$ and $U=V$, we have $U$
    is path-connected.

\end{solution}